Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-08-09 jap.manuscript.RMD
table and template updates

RESEARCH ARTICLE

@@

Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

Kristian Lian^1^, Sara Christine Olsen Moen^1^, Håvard Hamarsland^1^, Daniel Hammarström^1^, Stian Ellefsen^1^

@@

**Keywords:** Skeletal muscle; hypertrophy; resistance training; glucose; ribosome

@@

### Markers of ribosome biogenesis

##### Total RNA and ribosomal RNA

@@

##### Protein

@@

dxa.tab %>%
  full_join(humac.tab) %>%
  pivot_wider(values_from = mean,
              names_from = measure) %>%
  full_join(gendercount) %>%
  select(sex, n, age, height, weight, lm, isok.60, isok.240, isom) %>%

  ## Make it to flextable
  flextable() %>%
  ## Change headers
  compose(i = 1, j = c(1, 2, 3, 4, 5, 6, 7, 8, 9), part = "header", 
          value = c(as_paragraph("Sex"),
                    as_paragraph("n"), 
                    as_paragraph("Age (yrs)"), 
                    as_paragraph("Stature (cm)"), 
                    as_paragraph("Body mass (kg)"),
                    as_paragraph("Lean mass (kg)"),
                    as_paragraph("60\U00BA sec", as_sup("-1")), 
                    as_paragraph("240\U00BA sec", as_sup("-1")), 
                    as_paragraph("0\U00BA sec", as_sup("-1")))) %>%
  add_header_row(values = c(" ", "Knee-extension peak torque"), colwidths = c(6, 3)) %>%
  add_body_row(top = FALSE, value = as_paragraph("Values are mean and (SD)"), colwidths = 9) %>%
  set_caption("Table 1. Participant characteristics")

@@

## Flextable
tab.dat %>%
  flextable() %>%
  compose(i = 1, j = c(1, 2, 3, 4), part = "header",
          value = c(as_paragraph("Gene"),
                    as_paragraph("Sequence (forward - reverse)"),
                    as_paragraph("CT mean (SD)"),
                    as_paragraph("E"))) %>%
  #add_header_row(values = c(" ", " ", " ", "Primer sequences"), 
               #  colwidths = c(1, 1, 1, 1)) %>%
  set_caption("Table 2. Primer Sequences") %>%
  width(j = 1, 1.5, unit = "in") %>%
  width(j = 2, 3, unit = "in") %>%
  width(j = 3, 1.5, unit = "in") %>%
  width(j = 4, 0.5, unit = "in")
  #set_table_properties(layout = "autofit")

>>>>

##### RESEARCH ARTICLE

@@

#### Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

###### Kristian Lian^1^, Sara Christine Olsen Moen^1^, Håvard Hamarsland^1^, Daniel Hammarström^1^, Stian Ellefsen^1^

@@

**Keywords:** Glucose; hypertrophy; resistance training; ribosome; skeletal muscle

@@

## Markers of ribosome biogenesis

### Total RNA and ribosomal RNA

@@

### Protein

@@

dxa.flex <- dxa.tab %>%
  full_join(humac.tab) %>%
  pivot_wider(values_from = mean,
              names_from = measure) %>%
  full_join(gendercount) %>%
  select(sex, n, age, height, weight, lm, isok.60, isok.240, isom) %>%

  ## Make it to flextable
  flextable() %>%
  ## Change headers
  compose(i = 1, j = c(1, 2, 3, 4, 5, 6, 7, 8, 9), part = "header", 
          value = c(as_paragraph("Sex"),
                    as_paragraph("n"), 
                    as_paragraph("Age (yrs)"), 
                    as_paragraph("Stature (cm)"), 
                    as_paragraph("Body mass (kg)"),
                    as_paragraph("Lean mass (kg)"),
                    as_paragraph("60\U00BA sec", as_sup("-1")), 
                    as_paragraph("240\U00BA sec", as_sup("-1")), 
                    as_paragraph("0\U00BA sec", as_sup("-1")))) %>%
  add_header_row(values = c(" ", "Knee-extension peak torque"), colwidths = c(6, 3)) %>%
  set_caption("Table 1. Participant characteristics")

dxa.flex <- border(dxa.flex, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "grey"),
                     border.bottom = fp_border_default(color = "grey"),
                     border.left = fp_border_default(color = "grey"),
                     border.right = fp_border_default(color = "grey"),
                     part = "all")

dxa.flex

```
Values are means ± SD. 60º sec-1 = 60 degrees per second movement speed (isokinetic), 240º sec-1 = 240 degrees per second movement speed (isokinetic), 0º sec-1 = 0 degrees per second movement speed (isometric).

@@

## Flextable
primer.tab <- tab.dat %>%
  flextable() %>%
  compose(i = 1, j = c(1, 2, 3, 4), part = "header",
          value = c(as_paragraph("Gene"),
                    as_paragraph("Sequence (forward - reverse)"),
                    as_paragraph("Ct mean (SD)"),
                    as_paragraph("E"))) %>%
  set_caption("Table 2. Primer Sequences") %>%
  set_table_properties(layout = "autofit")

primer.tab <- border(primer.tab, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "grey"),
                     border.bottom = fp_border_default(color = "grey"),
                     border.left = fp_border_default(color = "grey"),
                     border.right = fp_border_default(color = "grey"),
                     part = "all")

primer.tab

```
Values of CT are means ± SD. rRNA = ribosomal RNA, E = primer efficiency. Average cycle thresholds (Ct) and priming efficiencies were calculated from all qPCR reactions.
